Building a GNU/Hurd Cluster

### 2018-01-28 slides/rpctrace.tex
rpctrace slides - add slide illustrating basic operation of rpctrace

>>>>

\task {rpctrace}{}{lr}{}

\task [right = of rpctrace] {Traced Task 2}{}{sl}{}
\task [above = of Traced Task 2] {Traced Task 1}{}{sl}{}
\task [below = of Traced Task 2] {Traced Task 3}{}{sl}{}

\task [above = of rpctrace] {Unknown Task}{}{sl}{}

\draw [port link] (rpctrace Left Port 0) -- +(-1,0) |- (Unknown Task Port 0);
\draw [port link] (Traced Task 2 Port 0) -- (rpctrace Right Port 0);
\draw [port link] (Traced Task 1 Port 0) -| ($(Traced Task 1 Port 0)!.5!(rpctrace Right Port 5)$) |- (rpctrace Right Port 5);
\draw [port link] (Traced Task 3 Port 0) -| ($(Traced Task 3 Port 0)!.5!(rpctrace Right Port -5)$) |- (rpctrace Right Port -5);

\node (Task 1 sendright) at (Traced Task 1 Port 0) [send, anchor=west] {S};
\node (Task 2 sendright) at (Traced Task 2 Port 0) [send, anchor=west] {S};
\node (Task 3 sendright) at (Traced Task 3 Port 0) [send, anchor=west] {S};

\node (Unknown Task recvright) at (Unknown Task Port 0) [recv, anchor=west] {R};

\node (R1) at (rpctrace Right Port 5) [recv, anchor=east] {R};
\node (R2) at (rpctrace Right Port 0) [recv, anchor=east] {R};
\node (R3) at (rpctrace Right Port -5) [recv, anchor=east] {R};

\node (S1) at (rpctrace Left Port 0) [send, anchor=west] {S};

\draw [internal link] (S1) -- (R2);
\draw [internal link] ($(S1)!.5!(R2)$) -- (R1);
\draw [internal link] ($(S1)!.5!(R2)$) -- (R3);
